\section{Dataset, Features, Labels}

The goal of our work is to find the verb relationship between a subject entity and an object entity. Hence to turn this into a classification task, verbs become labels. Subject, objects and their related attributes become features for classification.\\
\\
We used two different datasets for this classification task. Our ultimate goal is to classify the belief instances that we find in the \textbf{NELL SVO} dataset. This dataset contains ~220 million \emph{Subject Verb Object Count} tuples that have been mined by NELL. However we use another dataset: \textbf{NELL RTW} formalized dataset to give us metadata over the subjects and objects in the \textbf{NELL SVO} dataset. This dataset provides similar information in the form of \emph{Entity Relation Value} however, it provides hierarchical categories for each of the entities and values.\\
\\
The same belief in the two different datasets are represented differently:\\
In the SVO dataset:\\
\\
\emph{cat eat fish}\\
\\
In the RTW dataset:\\
\\
\emph{concept:animal:cat concept:animalseatfood concept:food:fish}\\
\\
We plan to use the categorical data from the \textbf{NELL RTW} dataset as supplementary features for subject and object, giving additional information for classification.\\ We can project the entities in the \textbf{NELL SVO} dataset onto the \textbf{NELL RTW} dataset to find what the categories for each individual subject and object are.\\
\\
We only looked at the tuples with categorical data that exists within the \textbf{NELL RTW} dataset. Of which we take 90\% of the data for training and 10\% of the data for testing, by sampling every 10 tuples putting 9 into training and 1 into testing. 